---
title: "Benefit Type Maps"
author: "Laurel Abowd"
date: "1/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(janitor)
library(here)
library(sf)
library(tmap)
library(terra)
library(raster)
library(kableExtra)
```

Data is in the GP Forest Folks folder under the survey/interviews tab - just copy the data folder w/in R data.

# Test to work with categorizing benefits

```{r include = FALSE}
benefits_test <- read_csv(here("data", "benefit_type_test.csv")) 
respondents <- read_csv(here("data", "Respondent_names.csv")) 
benefits_test <- merge(respondents, benefits_test)

```

### Take data from wide format with categories in columns to categories in rows and drop na values

```{r}
benefits_tidy <- benefits_test %>% 
  pivot_longer(!1:15, names_to = "Category") %>% drop_na()

```

### Convert benefits_tidy to shapefile

```{r}
benefits_tidy_sf <- benefits_tidy %>% 
  st_as_sf(wkt = "wkt", crs = 4326) %>% 
  select(-geojson)
```

### Map benefit categories

```{r}
ggplot(data = benefits_tidy_sf) +
  geom_sf(aes(geometry = wkt), alpha = 0.5) +
  facet_wrap(~ Category, ncol = 4)
```
### END TEST 

# Benefit categories

```{r}
benefits_categories <- read_csv(here("data", "benefits_categories.csv")) %>% slice(-1)
respondents <- read_csv(here("data", "Respondent_names.csv")) 
benefits_categories <- merge(respondents, benefits_categories)

```
### Take data from wide format with categories in columns to categories in rows and drop na values

```{r}
benefits_cat_tidy <- benefits_categories %>% 
  pivot_longer(!1:16, names_to = "Category") %>% drop_na(value) %>% 
  mutate(value = case_when(
    value == 1 ~"Primary",
    value == 2 ~ "Secondary"
  ))

```

```{r}
# Export benefits categories tidy file
# write_csv(benefits_cat_tidy, "benefits_categories_tidy.csv")
```


### Benefits with a value of 1 were listed as primary benefits
### Benefits with a value of 2 were listed as secondary or co-benefits 

```{r}
# Which benefits were listed most frequently?

benefit_frequencey <- benefits_cat_tidy %>% 
  group_by(Category) %>% 
  summarize(n = n()) %>% 
  arrange(-n)

# Visualize table. 

benefit_frequencey %>% 
  kable(col.names = c("Category", "Count")) %>% 
  kable_styling(bootstrap_options = "striped", full_width = FALSE)

```

```{r}
# What about when you account for primary vs. secondary benefits?
benefit_freq_order <- benefits_cat_tidy %>% 
  group_by(Category, value) %>% 
  summarize(n = n()) %>% 
  arrange(value, -n)

# Visualize table. 

benefit_freq_order %>% 
  kable(col.names = c("Category", "Primary / Secondary", "Count")) %>% 
  kable_styling(bootstrap_options = "striped", full_width = FALSE)

```

### Export tidy categories file


### Visualize benefits

### Convert benefits_tidy to shapefile

```{r}
benefits_cat_tidy_sf <- benefits_cat_tidy %>% 
  st_as_sf(wkt = "wkt", crs = 4326) %>% 
  dplyr::select(-geojson) 
```


### Map benefit categories

```{r fig.align= 'center'}
ggplot(data = benefits_cat_tidy_sf) +
  geom_sf(aes(geometry = wkt, fill = value), alpha = 0.5) +
  facet_wrap(~ Category, ncol = 8) 
```

### Raster maps of benefit count

```{r}
# Teale Albers projection in meters. 
#TA <- CRS("+proj=aea +lat_1=34 +lat_2=40.5 +lat_0=0 +lon_0=-120 +x_0=0 +y_0=-4000000 +datum=WGS84 +units=m")

# Create field in benefits_cat_tidy_sf (this is what rasterize will count)
benefits_cat_tidy_sf_field <- benefits_cat_tidy_sf %>% mutate("field" = 1) %>% st_transform(crs = 3310)

# Create raster template 
raster_template_benefit <- rast(ext(-139898.783514861, 151851.181894269, -211402.352889147, 317078.385940864), resolution = 1000, crs = st_crs(benefits_cat_tidy_sf_field)$wkt)
                                

# Create raster map with count of benefits (field)
#raster_benefts <- terra::rasterize(vect(benefits_cat_tidy_sf_field), raster_template_benefit,
                            #field = "field", fun = sum)
```

```{r}
#plot(raster_benefts)  ## Only get single raster
```

### Need to get each polygon as raster.

```{r}
benefits_individual <- split(benefits_cat_tidy_sf_field, benefits_cat_tidy_sf_field$wkt)

```

```{r}
# Create raster map with count of benefits (field)
# Sample for one row
raster_benefits_1 <- terra::rasterize(vect(benefits_cat_tidy_sf_field[1,]), raster_template_benefit)
```

```{r}
plot(raster_benefits_1*3) # checked raster math works
```

```{r}
# create empty raster stack to store objects
benefit_stack <- stack()


# Create loop to stack each raster layer (each individual polygon)
for (x in 1:171) {
  benefit_layer <- terra::rasterize(vect(benefits_cat_tidy_sf_field[x,]), raster_template_benefit)
  benefit_stack <- raster::stack(benefit_stack, as(benefit_layer, "Raster"))
}
```


```{r}
# Sum layers
benefits_sum_2 <- calc(benefit_stack, fun = sum, na.rm = TRUE) 

# Any raster cells with value of 0 become NA
benefits_sum_2[benefits_sum_2 == 0]<-NA

```

```{r}
# Plot summation 
plot(benefits_sum_2)
```
```{r}
# write raster file
# writeRaster(benefits_sum_2, "benefit_count.tif", overwrite=TRUE)
```

### Tmap of raster addition

```{r}
# TCSI boundary
tcsi <- st_read(here("data", "TCSI_boundary", "Tahoe-Central_Sierra_Initiative.shp"))

# Convert to TA crs
tcsi <- tcsi %>% 
  st_transform(crs = 3310)
```
```{r}
# Create basemap
library(basemaps)

tcsi_bbox = st_bbox(tcsi, crs = st_crs(tcsi))

# Increase size of bbox for space around edges
tcsi_bbox_large = st_bbox(st_buffer(st_as_sfc(tcsi_bbox), 15000)) 

basemap_gray <- basemap_raster(tcsi_bbox, map_service = "esri",
                                        map_type = "world_light_gray_base")

basemap_gray_large <- basemap_raster(tcsi_bbox_large, map_service = "esri",
                                        map_type = "world_light_gray_base")

```


```{r}
library(tmap)

tmap_mode(mode = "plot")

benefits_map_nolegend <- tm_shape(basemap_gray_large) +
  tm_rgb() +
tm_shape(benefits_sum_2) +
   tm_raster(palette = "inferno", alpha = 0.5,
             title="Benefit count",
             style = "cont",
             breaks = c(1, 10, 20, 30, 40)) +
tm_shape(tcsi) +
  tm_borders("black", lwd = 2) +
tm_layout(title = "Benefits", 
            title.position = c("right", "top"),
          title.size = 2,
          title.bg.color = "white",
          legend.show = FALSE,
          legend.bg.color = "white",
          frame = TRUE, frame.lwd = 2,
          legend.position = c("left", "bottom")) 

benefits_map_nolegend

#breaks = c(1, 5, 15, 25)

# tmap_save(benefits_map_nolegend, "benefits_map_count_nolegend_022422.png")
```

```{r}
tmap_mode(mode = "plot")
library(viridis)

tm_shape(basemap_gray_large) +
  tm_rgb() +
tm_shape(benefits_sum_2) +
   tm_raster(palette = "inferno", alpha = 0.5,
             title="Count",
             style = "cont",
             breaks = c(1, 10, 20, 30, 40),
             legend.is.portrait = FALSE) +
tm_shape(tcsi) +
  tm_borders("black", lwd = 2) +
#tm_layout(title = "TCSI Benefits", 
          #title.position = c("right", "top"),
          #title.size = 1.5,
          #title.bg.color = "white") +
  tm_layout(legend.bg.color = "white",
          frame = TRUE, frame.lwd = 2,
          legend.outside.position = "bottom",
          legend.outside = TRUE,
          legend.outside.size = 0.3, 
          legend.width = 1,
          legend.text.size = 1.5,
          legend.title.size = 2)

```





# Adverse impacts categories

```{r}
impacts_categories <- read_csv(here("data", "adverse_impacts_categories.csv"))
impacts_categories <- merge(respondents, impacts_categories)

```

### Take data from wide format with categories in columns to categories in rows and drop na values

```{r}
impacts_cat_tidy <- impacts_categories %>% 
  pivot_longer(!1:16, names_to = "Category") %>% drop_na(value)

```

### Impacts with a value of 1 were listed as primary impacts
### Impacts with a value of 2 were listed as secondary or impacts 

```{r}
# Which impacts were listed most frequently?

impact_frequencey <- impacts_cat_tidy %>% 
  group_by(Category) %>% 
  summarize(n = n()) %>% 
  arrange(-n)

# Visualize table. 

impact_frequencey %>% 
  kable(col.names = c("Category", "Count")) %>% 
  kable_styling(bootstrap_options = "striped", full_width = FALSE)

```

```{r}
# What about when you account for primary vs. secondary impacts?
impact_freq_order <- impacts_cat_tidy %>% 
  group_by(Category, value) %>% 
  summarize(n = n()) %>% 
  arrange(value, -n)

# Visualize table. 

impact_freq_order %>% 
  kable(col.names = c("Category", "Primary / Secondary", "Count")) %>% 
  kable_styling(bootstrap_options = "striped", full_width = FALSE)

```
### Visualize impacts

### Convert impacts_tidy to shapefile

```{r}
impacts_cat_tidy_sf <- impacts_cat_tidy %>% 
  st_as_sf(wkt = "wkt", crs = 4326) %>% 
  dplyr::select(-geojson) %>% 
  mutate(value = case_when(
    value == 1 ~"Primary",
    value == 2 ~ "Secondary"
  ))
```

```{r}
#impacts_cat_tidy <- impacts_cat_tidy %>% 
  #mutate(value = case_when(
    #value == 1 ~"Primary",
    #value == 2 ~ "Secondary"
  #))

# write_csv(impacts_cat_tidy, "impacts_categories_tidy.csv")
```


### Map impact categories

```{r fig.align='center'}
ggplot(data = impacts_cat_tidy_sf) +
  geom_sf(aes(geometry = wkt, fill = value), alpha = 0.5) +
  facet_wrap(~ Category, ncol = 7) 
```

### Adverse impacts raster map

```{r}
# Create field in benefits_cat_tidy_sf (this is what rasterize will count)
impacts_cat_tidy_sf_field <- impacts_cat_tidy_sf %>% mutate("field" = 1) %>% st_transform(crs = 3310)

# Create raster template 
raster_template_impacts <- rast(ext(-139898.783514861, 151851.181894269, -211402.352889147, 317078.385940864), resolution = 1000, crs = st_crs(impacts_cat_tidy_sf_field)$wkt)
```

```{r}
impacts_individual <- split(impacts_cat_tidy_sf_field, impacts_cat_tidy_sf_field$wkt)
```

```{r}
# create empty raster stack to store objects
impacts_stack <- stack()


# Create loop to stack each raster layer (each individual polygon)
for (x in 1:108) {
  impacts_layer <- terra::rasterize(vect(impacts_cat_tidy_sf_field[x,]), raster_template_impacts)
  impacts_stack <- raster::stack(impacts_stack, as(impacts_layer, "Raster"))
}
```


```{r}
# Sum layers
impacts_sum <- calc(impacts_stack, fun = sum, na.rm = TRUE) 

# Any raster cells with value of 0 become NA
impacts_sum[impacts_sum == 0]<-NA

```

```{r}
# Plot summation 
plot(impacts_sum)
```

### tmap of raster impacts

```{r}
library(tmap)

tmap_mode(mode = "plot")

impacts_map_nolegend <- tm_shape(basemap_gray_large) +
  tm_rgb() +
tm_shape(impacts_sum) +
   tm_raster(palette = "viridis", alpha = 0.5,
             title="Adverse impacts count",
             style = "cont",
             breaks = c(1, 5, 15, 25)) +
tm_shape(tcsi) +
  tm_borders("black", lwd = 2) +
tm_layout(title = "Adverse Impacts", 
          title.position = c("right", "top"),
          title.size = 2,
          title.bg.color = "white",
          legend.show = FALSE,
          legend.bg.color = "white",
          frame = TRUE, frame.lwd = 2,
          legend.position = c("left", "bottom")) 

impacts_map_nolegend

#breaks = c(1, 5, 15, 25)

#tmap_save(impacts_map_nolegend, "impacts_map_count_nolegend_022422.png")
```


# Threats categories

```{r}
threats_categories <- read_csv(here("data", "threats_categories.csv")) %>% slice(-1)
threats_categories <- merge(respondents, threats_categories)

```

### Take data from wide format with categories in columns to categories in rows and drop na values

```{r}
threats_cat_tidy <- threats_categories %>% 
  pivot_longer(!1:15, names_to = "Category") %>% drop_na(value)

```

```{r}
# Which threats were listed most frequently?

threat_frequencey <- threats_cat_tidy %>% 
  group_by(Category) %>% 
  summarize(n = n()) %>% 
  arrange(-n)

# Visualize table. 

threat_frequencey %>% 
  kable(col.names = c("Category", "Count")) %>% 
  kable_styling(bootstrap_options = "striped", full_width = FALSE)

```

### Visualize threats

### Convert threats_tidy to shapefile

```{r}
threats_cat_tidy_sf <- threats_cat_tidy %>% 
  st_as_sf(wkt = "wkt", crs = 4326) %>% 
  dplyr::select(-geojson) %>% 
  mutate(value = case_when(
    value == 1 ~"Primary"))
```

### Map impact categories

```{r fig.align='center'}
ggplot(data = threats_cat_tidy_sf) +
  geom_sf(aes(geometry = wkt, fill = value), alpha = 0.5) +
  facet_wrap(~ Category, ncol = 7) 
```

### Adverse impacts raster map

```{r}
# Create field in threats_cat_tidy_sf (this is what rasterize will count)
threats_cat_tidy_sf_field <- threats_cat_tidy_sf %>% mutate("field" = 1) %>% st_transform(crs = 3310)

# Create raster template 
raster_template_threats <- rast(ext(-139898.783514861, 151851.181894269, -211402.352889147, 317078.385940864), resolution = 1000, crs = st_crs(threats_cat_tidy_sf_field)$wkt)
```

```{r}
threats_individual <- split(threats_cat_tidy_sf_field, threats_cat_tidy_sf_field$wkt)
```

```{r}
# create empty raster stack to store objects
threats_stack <- stack()


# Create loop to stack each raster layer (each individual polygon)
for (x in 1:105) {
  threats_layer <- terra::rasterize(vect(threats_cat_tidy_sf_field[x,]), raster_template_threats)
  threats_stack <- raster::stack(threats_stack, as(threats_layer, "Raster"))
}
```

```{r}
# Sum layers
threats_sum <- calc(threats_stack, fun = sum, na.rm = TRUE) 

# Any raster cells with value of 0 become NA
threats_sum[threats_sum == 0]<-NA

```

```{r}
# Plot summation 
plot(threats_sum)
```

### tmap threats raster map

```{r}
library(tmap)

tmap_mode(mode = "plot")

threats_map_nolegend <- tm_shape(basemap_gray_large) +
  tm_rgb() +
tm_shape(threats_sum) +
   tm_raster(palette = "viridis", alpha = 0.5,
             title="Threats count",
             style = "cont",
             breaks = c(1, 5, 15, 25)) +
tm_shape(tcsi) +
  tm_borders("black", lwd = 2) +
tm_layout(title = "Threats", 
            title.position = c("right", "top"),
          title.size = 2,
          title.bg.color = "white",
          legend.show = FALSE,
          #legend.bg.color = "white",
          frame = TRUE, frame.lwd = 2)
          #legend.position = c("left", "bottom")) ) 

threats_map_nolegend

#tmap_save(threats_map_nolegend, "threats_map_count_nolegend_022422.png")
```

# Mgmt priority categories

```{r}
priorities_categories <- read_csv(here("data", "mgmt_prioritization_categories.csv")) 
priorities_categories <- merge(respondents, priorities_categories)

```

### Take data from wide format with categories in columns to categories in rows and drop na values

```{r}
priorities_cat_tidy <- priorities_categories %>% 
  pivot_longer(!1:15, names_to = "Category") %>% drop_na(value)

```

```{r}
# Which mgmt priorities were listed most frequently?

priorities_frequencey <- priorities_cat_tidy %>% 
  group_by(Category) %>% 
  summarize(n = n()) %>% 
  arrange(-n)

# Visualize table. 

priorities_frequencey %>% 
  kable(col.names = c("Category", "Count")) %>% 
  kable_styling(bootstrap_options = "striped", full_width = FALSE)

```

### Visualize mgmt priorities

### Convert priorities_tidy to shapefile

```{r}
priorities_cat_tidy_sf <- priorities_cat_tidy %>% 
  st_as_sf(wkt = "wkt", crs = 4326) %>% 
  dplyr::select(-geojson) %>% 
  mutate(value = case_when(
    value == 1 ~"Primary"))
```

### Map mgmt priorities

```{r fig.align='center'}
ggplot(data = priorities_cat_tidy_sf) +
  geom_sf(aes(geometry = wkt, fill = value), alpha = 0.5) +
  facet_wrap(~ Category, ncol = 7) 
```

### Mgmt prioties raster map

```{r}
# Create field in threats_cat_tidy_sf (this is what rasterize will count)
priorities_cat_tidy_sf_field <- priorities_cat_tidy_sf %>% mutate("field" = 1) %>% st_transform(crs = 3310)

# Create raster template 
raster_template_priorities <- rast(ext(-139898.783514861, 151851.181894269, -211402.352889147, 317078.385940864), resolution = 1000, crs = st_crs(priorities_cat_tidy_sf_field)$wkt)
```

```{r}
priorities_individual <- split(priorities_cat_tidy_sf_field, priorities_cat_tidy_sf_field$wkt)
```

```{r}
# create empty raster stack to store objects
priorities_stack <- stack()


# Create loop to stack each raster layer (each individual polygon)
for (x in 1:54) {
  priorities_layer <- terra::rasterize(vect(priorities_cat_tidy_sf_field[x,]), raster_template_priorities)
  priorities_stack <- raster::stack(priorities_stack, as(priorities_layer, "Raster"))
}
```

```{r}
# Sum layers
priorities_sum <- calc(priorities_stack, fun = sum, na.rm = TRUE) 

# Any raster cells with value of 0 become NA
priorities_sum[priorities_sum == 0]<-NA

```

```{r}
# Plot summation 
plot(priorities_sum)
```

### tmap priorities raster map

```{r}
library(tmap)

tmap_mode(mode = "plot")

priorities_map_nolegend <- tm_shape(basemap_gray_large) +
  tm_rgb() +
tm_shape(priorities_sum) +
   tm_raster(palette = "viridis", alpha = 0.5,
             title="Priorities count",
             style = "cont",
             breaks = c(1, 5, 15, 25)) +
tm_shape(tcsi) +
  tm_borders("black", lwd = 2) +
tm_layout(title = "Management Priorities", 
            title.position = c("right", "top"),
          title.size = 2,
          title.bg.color = "white",
          legend.show = FALSE,
          #legend.bg.color = "white",
          frame = TRUE, frame.lwd = 2)
          #legend.position = c("left", "bottom")) )) 

priorities_map_nolegend

#tmap_save(priorities_map_nolegend, "priorities_map_count_nolegend_022422.png")
```

