---
title: "Maps"
author: "Laurel Abowd"
date: "1/4/2022"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(janitor)
library(here)
library(sf)
library(rnaturalearth)
library(rgeos)
```

Data is in the GP Forest Folks folder under the survey/interviews tab - just copy the data folder w/in R data.

# Benefits

```{r}
benefits <- st_read(here("data", "Map area - Benefits", "Map area - Benefits - Polygons.shp"))
respondents <- read_csv(here("data", "Respondent_names.csv")) 
```


```{r}
names(respondents)[1] <- "responde"
benefits <- merge(benefits, respondents)

```


```{r include = FALSE}
ggplot(data = benefits) +
  geom_sf(aes(fill = Name, alpha = 0.5))
```


```{r include = FALSE}
library(tmap)

tmap_mode(mode = "view")

tm_shape(benefits) +
   tm_fill("Name", palette = "BuGn", alpha = 0.5)
```


```{r}
# Benefit area for each respondent
benefits_respondents <- benefits %>% 
  group_by(responde, Name) %>% 
  summarize("geometry" = st_union(geometry)) %>%  ungroup()
```

```{r include = FALSE}
julie <- benefits_respondents %>% 
  filter(Name == "Julie Fair")

allison <- benefits_respondents %>% 
  filter(Name == "Allison Thomson") 
```


```{r include = FALSE}
ggplot(data = benefits_respondents) +
  geom_sf(fill = "blue", alpha = 0.1)


ggplot() +
  geom_sf(data = julie, fill = "blue", alpha = 0.1) +
  geom_sf(data = allison, fill = "red", alpha = 0.1)
  
```

```{r}
library(rgeos)
# Respondents 
benefits_union <- gUnaryUnion(as_Spatial(benefits), id = benefits$Name) %>%  st_as_sf()
  
```

## Map of overlapping benefits
Each individual corresponds to one layer.

```{r}
library(tmap)

tmap_mode(mode = "view")

tm_shape(benefits_union) +
   tm_fill("blue", alpha = 0.1)
```


## Benefit responses
Hover over the map for individual responses.

```{r}
benefit_types <- read_csv(here("data", "benefits_responses.csv")) %>% slice(-1)
respondents_two <- read_csv(here("data", "Respondent_names.csv")) 
benefit_types <- merge(benefit_types, respondents_two)
```

```{r}
benefit_types_sf <- benefit_types %>% 
  st_as_sf(wkt = "wkt", crs = 4326) %>% 
  select(-geojson)
```


```{r}
library(tmap)

tmap_mode(mode = "view")

tm_shape(benefit_types_sf) +
   tm_fill("Name", palette = "Blues", alpha = 0.5, id = "What forest benefit does your organization value in this area?")
```


## Benefit responses by organization type

```{r}
library(tmap)

tmap_mode(mode = "view")

tm_shape(benefit_types_sf) +
   tm_fill("Type", palette = "Dark2", alpha = 0.2, id = "What forest benefit does your organization value in this area?")
```



# Adverse Impacts

```{r}
impacts <- st_read(here("data", "Map area - Adverse Impacts from Disturbances", "Map area - Adverse Impacts from Disturbances - Polygons.shp"))

impacts <- merge(impacts, respondents)
```

## Map of overlapped impacts
Each individual corresponds to one layer.

```{r}
impacts_union <- gUnaryUnion(as_Spatial(impacts), id = impacts$Name) %>%  st_as_sf()
```
```{r}
library(tmap)

tmap_mode(mode = "view")

tm_shape(impacts_union) +
   tm_fill("goldenrod", alpha = 0.2)
```

## Impact responses
Hover over the map for individual responses.
```{r}
impact_types <- read_csv(here("data", "adverse_impacts_responses.csv")) %>% slice(-1)
impact_types <- merge(impact_types, respondents_two)

```

```{r}
# convert impact responses to sf
impact_types_sf <- impact_types %>% 
  st_as_sf(wkt = "wkt", crs = 4326) %>% 
  select(-geojson)
```

```{r}
library(tmap)

tmap_mode(mode = "view")

tm_shape(impact_types_sf) +
   tm_fill("Name", palette = "YlOrRd", alpha = 0.2, id = "What would the adverse impact from disturbance be in this area?")
```

# Threats

```{r}
threats <- st_read(here("data", "Map area - Threats", "Map area - Threats - Polygons.shp"))

threats <- merge(threats, respondents)
```

## Map of overlapping threats
Each individual corresponds to one layer.

```{r}
threats_union <- gUnaryUnion(as_Spatial(threats), id = threats$Name) %>%  st_as_sf()
```
```{r}
library(tmap)

tmap_mode(mode = "view")

tm_shape(threats_union) +
   tm_fill("red", alpha = 0.1)
```

## Threat responses
Hover over the map for individual responses.

```{r}
threat_types <- read_csv(here("data", "threats_responses.csv")) %>% slice(-1)
threat_types <- merge(threat_types, respondents_two)
```
```{r}
# convert threat responses to sf
threat_types_sf <- threat_types %>% 
  st_as_sf(wkt = "wkt", crs = 4326) %>% 
  select(-geojson)
```

```{r}
library(tmap)

tmap_mode(mode = "view")

tm_shape(threat_types_sf) +
   tm_fill("Name", palette = "Reds", alpha = 0.2, id = "What damages would a disturbance cause in this area?")
```

# Management Priorities

```{r}
priorities <- st_read(here("data", "Map area - Management Prioritization", "Map area - Management Prioritization - Polygons.shp"))

priorities <- merge(priorities, respondents)

```
## Map of overlapping management priority areas
Each individual corresponds to one layer.

```{r}
priorities_union <- gUnaryUnion(as_Spatial(priorities), id = priorities$Name) %>%  st_as_sf()
```
```{r}
library(tmap)

tmap_mode(mode = "view")

tm_shape(priorities_union) +
   tm_fill("purple", alpha = 0.1)
```
## Priority responses
Hover over the map for individual responses.
```{r}
priority_types <- read_csv(here("data", "priorities_responses.csv")) %>% slice(-1)
priority_types <- merge(priority_types, respondents_two)
```

```{r}
# convert priority responses to sf
priority_types_sf <-priority_types %>% 
  st_as_sf(wkt = "wkt", crs = 4326) %>% 
  select(-geojson)
```

```{r}
library(tmap)

tmap_mode(mode = "view")

tm_shape(priority_types_sf) +
   tm_fill("Name", palette = "BuPu", alpha = 0.2, 
           id = "Why would you prioritize forest management in this area? What forest benefit does your organization value in this area?")
```

## Priority response by org type

```{r}
library(tmap)

tmap_mode(mode = "view")

tm_shape(priority_types_sf) +
   tm_fill("Type", palette = "Dark2", alpha = 0.2, 
           id = "Why would you prioritize forest management in this area? What forest benefit does your organization value in this area?")
```

